---
title: "Pre-Registration"
author: "Friederike Vorwerk"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE,
                      cache.lazy=FALSE)
```

# Dependencies
```{r}
# package vector
packages <- c("lmtest", "stats", "car", "nortest")

# un-comment to install packages
# for (i in 1:length(packages)){install.packages(packages[i], character.only = T)
# }

# load packages
for (i in 1:length(packages)){
  library(packages[i], character.only = T)
}
```

# Hypothesis 1: Covariance Analysis
```{r}

mat <- matrix(c(1/2, -1/3, -1/3, -1/3, 1/2))
contrasts(data$group) <- mat

#Estimate Model
symbgroup_model <- lm(symb_trust ~ group,
               data = symbgroup_data)

summary(symbgroup_model)
```

## Assumptions for Hypothesis 1

### Visual Assumption Checks
- linearity, homoscedasticity, outliers (row #)
- normal distribution
- homoscedasticity, outliers (even scattering?)
```{r}
plot(symbgroup_model)
```

## Outliners and influential cases
```{r}
# outliers
symbgroup_data$standardized_residuals <- rstandard(symbgroup_model) # should be <|2|
symbgroup_data$studentized_residuals <- rstudent(symbgroup_model) # should be <|3|

# influential cases
symbgroup_data$cooks_distance <- cooks.distance(symbgroup_model) # should be < 1
symbgroup_data$dfbeta <- dfbeta(symbgroup_model)
symbgroup_data$dffit <- dffits(symbgroup_model)
symbgroup_data$leverage <- hatvalues(symbgroup_model) # should be < 3 or 2 times as large as the average leverage (k+1/n)
symbgroup_data$covariance_ratios <- covratio(symbgroup_model) # within > 1 + [3(k + 1)/n] or > 1 + [3(k + 1)/n]

#write table
write.table(symbgroup_data, "../results/Symbol_trust_reaction_time_with_case_diagnostics.dat", sep ="\t", row.names = F)
```

### Identify cases
```{r}
# large residuals
symbgroup_data$large_residuals <- symbgroup_data$standardized_residuals > 2 | se_regression_data$standardized_residuals < -2
symbgroup_data[symbgroup_data$large_residuals,]
# expect 95% of cases to have standardized residuals within about |2|
# and 99% should lie within |2.5|

# influential cases (only for cases for which large_residual is TRUE)
symbgroup_data[symbgroup_data$large_residuals, c("cooks_distance", "leverage", "covariance_ratios")]
```
###Homoscedasiticty
```{r}
# Breusch Pagan Test / Cook-Weisberg Test: non-significance is homoscedastic
ncvTest(symbgroup_model)
```

### Independent Errors
```{r}
# Durbin-Watson Test: close value to 2 is good vs. <1 or >3 not good; non-significance is looked for
dwt(symbgroup_model)
```

### Normal distribution of residuals
```{r}
# Lilliefors test: non-significance in ND
lillie.test(resid(symbgroup_model))

# QQ plot with confidence intervals
qqPlot(symbgroup_model)

# density pot of student residuals
plot(density.default(x = symbgroup_data$studentized_residuals))
```

### No Multicollinearity of predictors
```{r}
# variance inflation factor
vif(symbgroup_model) # high values (e.g. 10) are problematic
mean(vif(symbgroup_model)) # average VIF > 1 regression may be biased
# tolerance: close to 1 means predictors are un-correlated, <.2 problematic
1/vif(symbgroup_model)
```



# Hypothesis 2: model comparison, likelihood ratio test
```{r}
model0 <- glm(system_trust ~ 1, data=data)
model1 <- glm(system_trust ~ symbol_trust, data=data)

# Likelihood Ratio Test
lrtest(model0,model1)
```



# Hypothesis 3: linear regression
```{r}
#modeling
reactiontrust_model <- lm(reaction_data  ~ symb_trust, data = reaction_data)
summary(reactiontrust_model)
```
##Assumptions of Linear Regression
- linearity
- normality of residuals
- homoscedasticity
- independent errors

### Visual Assumption Checks
```{r}
plot(reactiontrust_model)
```

##outliners and influential cases hypothesis 3
```{r}
# outliers
reaction_data$standardized_residuals <- rstandard(reactiontrust_model) # should be <|2|
reaction_data$studentized_residuals <- rstudent(reactiontrust_model) # should be <|3|

# influential cases
reaction_data$cooks_distance <- cooks.distance(reactiontrust_model) # should be < 1
reaction_data$dfbeta <- dfbeta(reactiontrust_model)
reaction_data$dffit <- dffits(reactiontrust_model)
reaction_data$leverage <- hatvalues(reactiontrust_model) # should be < 3 or 2 times as large as the average leverage (k+1/n)
reaction_data$covariance_ratios <- covratio(reactiontrust_model) # within > 1 + [3(k + 1)/n] or > 1 + [3(k + 1)/n]

# write table
write.table(reaction_data, "../results/Reaction_time_model_with_case_diagnostics.dat", sep ="\t", row.names = F)
```

### then identify cases
```{r}
# large residuals
reaction_data$large_residuals <- reaction_data$standardized_residuals > 2 | se_regression_data$standardized_residuals < -2
reaction_data[reaction_data$large_residuals,]
# expect 95% of cases to have standardized residuals within about |2|
# and 99% should lie within |2.5|

# influential cases (only for cases for which large_residual is TRUE)
reaction_data[reaction_data$large_residuals, c("cooks_distance", "leverage", "covariance_ratios")]
```

### Homoscredasiticty
```{r}
# Breusch Pagan Test / Cook-Weisberg Test: non-significance is homoscedastic
ncvTest(reactiontrust_model)
```

### Independent Errors
```{r}
# Durbin-Watson Test: close value to 2 is good vs. <1 or >3 not good; non-significance is looked for
dwt(reactiontrust_model)
```

### Normal distribution of residuals
```{r}
# Lilliefors test: non-significance in ND
lillie.test(resid(reactiontrust_model))

# QQ plot with confidence intervals
qqPlot(reactiontrust_model)

# density pot of student residuals
plot(density.default(x = reaction_data$studentized_residuals))
```
